ms_figures

### 2023-01-20 ms_figures.Rmd
new pipeline for preparing manuscript ms results and ms figures

```{r load_data}
# Set directories
datadir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/20220111"
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/outputs_20220111"

@@

>>>>

```{r load_data}
# Set directories
datadir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/20220111"
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/outputs_20220111"
```

@@

```{r ldc_net_exports_habitat_method}
ldc_net_habitat_method_summary <- read.csv(file.path(datadir, "ldc_net_habitat_method_summary.csv"))

ldc_net_exports_by_source_plot <- ldc_net_habitat_method_summary %>%
  ggplot(aes(x = year, y = net_export/1000000, color = habitat_method)) +
  geom_line() +
  scale_color_manual(values = habitat_source_colors) +
  labs(x = "", y = "Net export (million t)", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")

ldc_net_exports_by_source_plot
```

```{r trade_concentration_n_countries}
# Concentration of trade by production source, measured as the number of countries comprising 75%

export_n_countries_concentration <- read.csv(file.path(datadir, "export_concentration_n_countries_by_source.csv"))
import_n_countries_concentration <- read.csv(file.path(datadir, "import_concentration_n_countries_by_source.csv"))

export_n_countries_by_source_plot <- export_n_countries_concentration %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_line() +
  scale_color_manual(values = habitat_source_colors) +
  geom_line(data = export_concentration_n_countries, aes(x = year, y = n), color = "black") +
  labs(x = "", y = paste("Number of countries comprising ", cumulative_percent_threshold, "% of exports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw()

export_n_countries_by_source_plot

import_n_countries_by_source_plot <- import_n_countries_concentration %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_line() +
  scale_color_manual(values = habitat_source_colors) +
  geom_line(data = import_concentration_n_countries, aes(x = year, y = n), color = "black") +
  labs(x = "", y = paste("Number of countries comprising ", cumulative_percent_threshold, "% of imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw()

import_n_countries_by_source_plot
```
